---
title: "Seeing is believing"
subtitle: "Support materials for conversation with Million Tutor Moves Observatories Team"
author: Rick Gilmore
date: 2024-04-12
execute:
  freeze: auto
format: 
  html:
    toc: true
    toc-depth: 3
    toc-location: right
    code-links:
      - text: "This demo"
        icon: github
        href: https://github.com/gilmore-lab/million-tutor-observatories
      - text: "databraryr"
        href: https://databrary.github.io/databraryr
    other-links:
      - text: "DeLoache et al."
        href: https://doi.org/10.17910/B7H019
      - text: "Databrary.org"
        href: https://databrary.org
---

## About

This page provides supplemental material for the conversation with the Million Tutor Moves Observatories project group on 2024-04-12.

## Set-up

Install the development version of *databraryr* if needed.
By default the `eval: false` option in the code chunk means that the chunk will not be evaluated.

```{r}
#| eval: false
pak::pak("databrary/databraryr")
```

## Log-in

```{r}
drq <- databraryr::make_default_request()
databraryr::login_db(email = Sys.getenv("DATABRARY_LOGIN"), store = TRUE, rq = drq)
```

## Retrieve data

DeLoache, J. (2014). Scale errors offer evidence for a perception-action dissociation early in life. *Databrary*. Retrieved April 11, 2024 from <http://doi.org/10.17910/B7H019>.

```{r}
v61_assets <- databraryr::list_volume_assets(vol_id = 61, rq = drq)
v61_assets
```

Download videos to local folder.

::: {.callout-warning}

When downloading identifiable data, it's important to add the target directory (here `mp4/`) to the appropriate `.gitignore` file.

:::

```{r}
downloaded_fns <- v61_assets |>
  dplyr::filter(format_extension == "mp4") |> # Not needed here, but handy
  databraryr::download_session_assets_fr_df(target_dir = "mp4", 
                                            overwrite = TRUE,
                                            make_portable_fn = TRUE, rq = drq)

downloaded_fns
```

::: {.callout-note}

Looks like I need to clean-up the file name cleaning function used by the `make_portable_fn` parameter.
There are duplicate underscores.

Also, the 9850 is the session identifier.

:::

## Embed videos

### `{r} downloaded_fns[1]`

{{< video `{r} downloaded_fns[1]` >}}

### `{r} downloaded_fns[2]`

{{< video `{r} downloaded_fns[2]` >}}

### `{r} downloaded_fns[3]`

{{< video `{r} downloaded_fns[3]` >}}

### `{r} downloaded_fns[4]`

{{< video `{r} downloaded_fns[4]` >}}

### `{r} downloaded_fns[5]`

{{< video `{r} downloaded_fns[5]` >}}

### `{r} downloaded_fns[6]`

{{< video `{r} downloaded_fns[6]` >}}

## Log-out

```{r}
databraryr::logout_db(rq = drq)
```
