---
title: "Databrary & Million Tutor Moves Observatories"
author: Rick Gilmore
date: 2024-04-12
execute:
  freeze: auto
format:
  html:
    repo-url: gilmore-lab/million-tutor-observatories
    repo-actions: [edit, issue]
    toc: true
    toc-depth: 3
    toc-location: right
---

## About

This page provides supplemental material for the conversation with the Million Tutor Moves Observatories project group on 2024-04-12.

## Set-up

Install the development version of *databraryr* if needed.
By default the `eval: false` option in the code chunk means that the chunk will not be evaluated.

```{r}
#| eval: false
pak::pak("databrary/databraryr")
```

## Log-in

```{r}
drq <- databraryr::make_default_request()
databraryr::login_db(email = Sys.getenv("DATABRARY_LOGIN"), store = TRUE, rq = drq)
```

## Retrieve data from volume 61

DeLoache, J. (2014). Scale errors offer evidence for a perception-action dissociation early in life. *Databrary*. Retrieved April 11, 2024 from <http://doi.org/10.17910/B7H019>.

```{r}
v61_assets <- databraryr::list_volume_assets(vol_id = 61, rq = drq)
```

Download videos to local folder.

```{r}
downloaded_fns <- v61_assets |>
  dplyr::filter(format_extension == "mp4") |>
  databraryr::download_session_assets_fr_df(target_dir = "mp4", 
                                            overwrite = TRUE,
                                            make_portable_fn = TRUE, rq = drq)

downloaded_fns
```

::: {.callout-note}

Looks like I need to clean-up the file name cleaning routine used by the `make_portable_fn` parameter.

:::

## Embed videos

### `{r} downloaded_fns[1]`

{{< video mp4/9850/Scale_error_with_car.mp4 >}}

### `{r} downloaded_fns[2]`

{{< video mp4/9850/Scale_error_with_chair.mp4 >}}

### `{r} downloaded_fns[3]`

{{< video mp4/9850/Scale_error_with_car__child_removes_shoe_.mp4 >}}

### `{r} downloaded_fns[4]`

{{< video mp4/9850/Scale_error_with_chair__2nd_example_.mp4 >}}

### `{r} downloaded_fns[5]`

{{< video mp4/9850/Scale_error_with_slide.mp4 >}}

### `{r} downloaded_fns[6]`

{{< video mp4/9850/Scale_error_with_slide__2nd_example_.mp4 >}}

## Log-out

```{r}
databraryr::logout_db(rq = drq)
```
